An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-27 paper.tex
Update placeholder about internet-drafts

%..................................................................................................
\pb{RFC Publication Rate:}
In total, 8,711 RFCs have been published through to the end of 2020.
Figure~\ref{fig:rfcs_by_area} shows how publication trends, in terms of
IETF areas and non-IETF streams, have changed over time. We identify three
broad publication phases in the RFC series. First, in 1969 through 1974,
RFCs are published at a rapid rate during the initial development of the
ARPANET. Then, from 1975 through 1985, development slows. This reflects a
relatively small community that is gaining real-world experience with the
network and developing a small core of applications and protocols. Finally,
with the creation of the IETF and the introduction of the National Science
Foundation Network (NSFNET) in 1986, both the community, and the number of
RFCs published, starts to expand rapidly. This is further driven by the
opening of the network to commercial and public use in the mid-1990s, and
continues to this day.

As shown, the annual RFC publication rate was highest in 2005, at the peak
of the standardisation efforts for SIP and related standards for voice-over-IP
and Internet telephony. The rate of publication has slowed in recent years,
following the completion of large work programmes relating to HTTP/2 and
WebRTC.

@@

\todo{Add draft publication count as mentioned in Section \ref{sec:org-dynamics:participants}}

>>>>

%..................................................................................................
\pb{RFC Publication Rate:}
In total, 8,711 RFCs have been published through to the end of 2020.
Figure~\ref{fig:rfcs_by_area} shows how publication trends, in terms of
IETF areas and non-IETF streams, have changed over time. We identify three
broad publication phases in the RFC series. First, in 1969 through 1974,
RFCs are published at a rapid rate during the initial development of the
ARPANET. Then, from 1975 through 1985, development slows. This reflects a
relatively small community that is gaining real-world experience with the
network and developing a small core of applications and protocols. Finally,
with the creation of the IETF and the introduction of the National Science
Foundation Network (NSFNET) in 1986, both the community, and the number of
RFCs published, starts to expand rapidly. This is further driven by the
opening of the network to commercial and public use in the mid-1990s.
The annual RFC publication rate was highest in 2005, at the peak
of the standardisation efforts for SIP and related standards for voice-over-IP
and Internet telephony. The rate of publication has slowed in recent years,
following the completion of large work programmes relating to HTTP/2 and
WebRTC.

@@

In addition to the published RFCs, we track work-in-progress documents,
known as Internet-drafts, that are intended for eventual publication as
RFCs.
\todo{Add internet-draft counts over time as mentioned in Section \ref{sec:org-dynamics:participants}}
